LAs_clusters k = 9

### 2021-03-11 src/LAs_Clusters_k9.Rmd
no prof

>>>>

## Auxiliary regression, dep. var.: upload clusters, NO PROF

```{r upload regression no prof, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

aux.up <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + admin + caring + plant +
                     earnings + I(total.busi/pop) + nvq4 + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

stargazer(aux.up, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
            "pop, 2018",
            #"pop. density, 2018",
            "job density, 2018",
            "distance to nearest met. area",
            "distance to London",
            "South of the UK",
            "% of managerial jobs, 2020",
            "% of tech jobs, 2020",
            "% of skilled trade jobs, 2020",
            #"% of professional jobs, 2020",
            "% of administrative jobs, 2020",
            "% of leisure jobs, 2020",
            "% of machine operation jobs, 2020",
            "earnings, 2019",
            "n. business est. per hab., 2019",
            "% of NVQ4+",
            "% furloughed pop., 2020",
            "n. of AM broadband tests per hab., 2020",
            "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs
                              , n.obs, n.obs))))
